---
title: "Regression models - Peer review"
author: "João Pedro Schmitt"
date: "31 de outubro de 2016"
output: html_document
---

### Introduction

A study for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, was explored the relationship between a set of variables and miles per gallon (MPG) (outcome). The particularly interested were following two questions:

* *Is an automatic or manual transmission better for MPG*
* *Quantify the MPG difference between automatic and manual transmissions*

### Prepare the enviroment

For this work, was used the dataset mtcars, available in the package *datasets*. The code below demonstre the setup:

```{r message=FALSE}
require(datasets)
require(graphics)
require(ggplot2)
require(MASS)
data("mtcars")
head(mtcars)
```

### Finding the relationship

The code below creates a linear model using *mpg* as outcome and only *am* as predictor:
```{r}
fit1 <- lm(mpg ~ am, data = mtcars)
print(summary(fit1)$coef)
print(summary(fit1)$r.squared)
```

In the summary above we can observe that for an automatic car we have the slope beeing zero with the intercept of miles per galon around 17.417 and when we have a manual car we have the increase of 7.245 in miles per galon. The P-value is significative because is less than 5% (0.05), so we can ignore the null hypothesis that the coeficients are zero. The current model explain 35.98% of the variance.

The best model is identified by *Final Model* (mpg ~ wt + qsec + am), using stepAIC that compares the p-values and r-squared of the predictors for each interaction:
```{r results='hide'}
fit2 <- stepAIC(lm(mpg ~ ., data = mtcars), direction="both")
```
```{r echo=FALSE}
summary(fit2)$call
```

The new model has the R-squared explained 84.97% compared with the old model that explain 35.98% doing the new model much more significative.

```{r}
print(summary(fit2)$coef)
print(summary(fit2)$r.squared)
```

Comparing the relevance of the new model, the new model is much more significative (p-value is 1.55e-09) and we can ignore the null hypothesis of use the old model.

```{r}
anova(fit1, fit2)
```

### Conclusion

We concluded that for estimate the consumption of miles per galon for a car, not only the transmission is relevant but the 1/4 mile time and the weight of the car are very important to obtain more precise results. 
Using the best model we can see that cars that has automatic transmission have a increase of 2.9358 at miles per gallon.

### Appendix

#### Exploratory data analisys about Miles per gallon vs transmission type. 

The plot shows that apparently the manual transmission has a better consumption of miles per gallons compared with a automatic transmission:
```{r fig.align='center', fig.width=5, fig.height=5}
boxplot(mpg ~ am, mtcars)
```

#### Residuals of model (mpg ~ am)

The analysis of the residuals in the plot below, has some points that are over others points, and in this linear model it is difficult to estimate a good mpg for a given car

```{r}
plot(fit1, which = 1)
```

#### Residuals of model (mpg ~ wt + qsec + am)

This residual plot is more reasonable with the less difference in the values compared with model (mpg ~ am), explainning better the fitted values.

```{r}
plot(fit2, which = 1)
```