---
title: "Regression models - Peer review"
author: "João Pedro Schmitt"
date: "31 de outubro de 2016"
output: html_document
---

### Instructions

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* *Is an automatic or manual transmission better for MPG*
* *Quantify the MPG difference between automatic and manual transmissions*

## Motor Trend Car Road Tests

The dataset used in this work is *mtcars*, this dataset has data extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

The variables of the *mtcars* are:

1. **mpg** = Miles/(US) gallon
2. **cyl** = Number of cylinders
3. **disp** = Displacement (cu.in.)
4. **hp** = Gross horsepower
5. **drat** = Rear axle ratio
6. **wt** = Weight (1000 lbs)
7. **qsec** = 1/4 mile time
8. **vs** = V/S
9. **am** = Transmission (0 = automatic, 1 = manual)
10. **gear** = Number of forward gears
11. **carb** = Number of carburetors

## Prepare the enviroment

For this work, was used the dataset mtcars, available in the package *datasets*. The code below demonstre the setup:

```{r}
# Load the dataset
library(datasets)
data("mtcars")

# Load libraries
require(graphics)
```

The dataset dimension of rows x columns:
```{r}
# Dimensions
dim(mtcars)
```

The dataset characteristics:
```{r}
# A little view
str(mtcars)
```

## Linear model 1

The code below creates a linear model using *mpg* as outcome and only *am* as predicator:
```{r}
fit <- lm(mpg ~ am, data = mtcars)
summary(fit)
```

In the summary above we can observe that for an automatic car we have the slope beeing zero with the mean of miles per galon around 17.417 and when we have a manual car we have the increase of 7.245 in miles per galon. The P-value is very significative because is less than 5% (0.05), so we can ignore the null hypothesis that the coeficients are zero.


